Measuring the Price of Anarchy in Critical Care Unit Interactions

### 2016-03-15 Reviews/response.tex

Below we respond to each reviewer in detail.

\subsection{Reviewer 1}

\begin{quote}
    \begin{textit}{
Write the clarifications of notations \(\lambda_{h}^{(l,h)},\lambda_{h}^{(l,l)}\). One \(h \in (NH,RG)\) other \(h\) denotes RG experiences high demand.
    }\end{textit}
\end{quote}

Thank you to the reviewer for noticing this detail.
We have changed all occurrences of \(h\) denoting an element of \(\NH, \RG\) to
be \(H\). This clarifies the paper.

@@

\begin{quote}
    \begin{textit}{
Give explanation for figure 3.
    }\end{textit}
\end{quote}

Another pointer in the text to the Figure has been added (``The transition rates are given by (2) and are illustrated diagrammatically in Figure 3"). This Figure is meant to illustrate diagrammatically the state space and transitions.

@@

\begin{quote}
    \begin{textit}{
    Write clearly major contribution of the paper corresponding to the existing
    literature.
    }\end{textit}
\end{quote}

\begin{quote}
    \begin{textit}{
    State clearly the objectives of the model.
    }\end{textit}
\end{quote}

The following paragraph is in the introduction of the paper: if the reviewer does not find it sufficient we would gladly clarify it further. At present we feel that it very clearly places the contribution of the paper (as highlighted by the 3rd reviewer) and also highlights what the main finding/objective of the model is.

``
The work presented in this paper contributes to the growing body of literature by applying state dependent queueing models in a game theoretical context to CCU interaction.
In particular this consideration allows for the investigation of targets imposed by central control [4].
The findings of this work justify and identify a choice of targets that align the interests of the individual hospitals with social welfare.
''

@@

\subsection{Reviewer 2}

\begin{quote}
    \begin{textit}{
    On page 5, the model is referred to as a Figure 6. This confuses and leaves a question on whether it is a figure or equations. I am unsure whether figure 6 is missing or authors are referring to the model on page 6.
    }\end{textit}
\end{quote}

This has now been fixed: the optimisation problem that defines the game is now
in a section with title: `Optimisation problem' and is referred to by a
labelling equation number. This was suggested by another reviewer and we feel
improves the paper.

@@

\begin{quote}
    \begin{textit}{
The paper is unreadable. The unknowns used, some, are undefined, for example on page 3, h, ch, etc are not defined and it is very difficult to find definitions of those defined. I suggest that the authors provide a list of the parameters used somewhere in the paper where it is easy to refer.
    }\end{textit}
\end{quote}

We were disappointed by this comment. To suggest that the paper is unreadable
is an exaggeration. Perhaps the reviewer did not have time to read page
2 which contained a table that clearly listed the variables they mention?

If we have misunderstood and that table is not sufficient we would gladly list
the variables with their definitions in a format more pleasing to the referee.
Although we note that the other two reviewers, one of which has clearly read
the paper carefully did not find the paper unreadable.

@@

\begin{quote}
    \begin{textit}{
    On page 12, authors states that ``It is also noted that as demand increases the effect of uncoordinated behaviour increases (and the recommended target also increases) as shown in Figure 13'', is there any possible explanation to this finding.
    }\end{textit}
\end{quote}

At present it is merely an observation from the emergent behaviour of the model however a sentence has been added:

``
It is also noted that as demand increases the effect of uncoordinated behaviour increases (and the recommended target also increases) as shown in Figure 12. This is potentially due to the fact that as demand increases there is the scope for larger discrepancy between optimal and sub optimal behaviours.
''

@@

\begin{quote}
    \begin{textit}{
    Are the Queuing and Game theoretic models never been implemented to solve such problems? There is a need to review literature that has information on application of the used models to hospital problems or related problems.
    }\end{textit}
\end{quote}

\begin{quote}
    \begin{textit}{
The authors need to give a justification on the reason why they are implementing the models.
    }\end{textit}
\end{quote}

It seems that the reviewer did indeed not read page 2 of the manuscript. As highlighted by the 3rd reviewer a literature review is present. This literature review highlights that there is not much work at the intersection of game theory, queueing theory and healthcare.

Furthermore the contributions and goals of the model are very clearly stated on page 2 and again highlighted in the conclusion section. If the reviewer could clarify there expectations if this is not sufficient we would gladly highlight the contributions of the paper (as recognized by the referees that have read it) further.

``
The work presented in this paper contributes to the growing body of literature by applying state dependent queueing models in a game theoretical context to CCU interaction.
In particular this consideration allows for the investigation of targets imposed by central control [4].
The findings of this work justify and identify a choice of targets that align the interests of the individual hospitals with social welfare.
''

@@

\begin{quote}
    \begin{textit}
        {
        The optimisation problem is shown as a figure (Figure 6). I suggest
        that this be separated from the text with a header such as
        ``Optimisation Problem" (much like a theorem).  Calling it a figure
        seems like a misnomer, and for me, actually made it harder to find.
        }
    \end{textit}
\end{quote}

This has been changed:

\begin{itemize}
    \item The figure has been changed to a section with a header as suggested.
    \item A label (3) has been added for easier reference throughout the text.
\end{itemize}

\begin{quote}
    \begin{textit}
        {
            In Figure 7, the caption should state which points are \(f_{NH}\) and
            which are \(F_{RG}\).
        }
    \end{textit}
\end{quote}

@@

``
... This optimal throughput \(T^*\) is
independent of \(t\).

Note that intuitively it could be thought that \(T^*\) is obtained when
\(K_{\NH}=c_{\NH}\) and \(K_{\RG}=c_{\RG}\) however this is not always the case
(numerical experiments have been carried out to verify this).
''

\begin{quote}
    \begin{textit}
        {
The authors make extensive use of bullets in the text. While bullets
can be useful to draw attention to key points, they can lead to lazy
writing. In my view, converting some of the bullet lists would improve
the clarity of the exposition.
        }
    \end{textit}
\end{quote}

3 of the 5 bullet point lists have been changed to be paragraphs. We felt that
this left a nice balance but if the reviewer feels strongly about this, we
would be happy to change the remaining bullet point lists.
\end{document}

### 2016-03-15 Paper/paper.tex
minor (pointers to figures and removing bulet points)

The paper is organised as follows:
\begin{itemize}
    \item Section \ref{queueingandgamemodels} presents the general methodology as well as a theoretical existence condition for Nash Equilibrium;
    \item Section \ref{results} presents the findings from two models;
    \item Conclusions and further ideas for progression are given in Section \ref{conclusions}.
\end{itemize}

@@

The state space for the Markov chain is given by:

@@

The stochastic transition rate matrix $Q=Q(c_{NH},c_{RG})$ of the continuous-time Markov chain \cite{Stewart2009} has entries $q_{ij}=q_{(u_i,v_i),(u_j,v_j)}$ which is the rate at which a transition from state $i$ to state $j$ occurs. The transition rates are given by:

\begin{equation}
q_{(u_i,v_i),(u_j,v_j)}=\begin{cases} u\mu_{\NH} & \text{ if  } (u_i,v_i)-(u_j,v_j)=(1,0),\\
 v\mu_{\RG} & \text{ if  } (u_i,v_i)-(u_j,v_j)=(0,1),\\
 \lambda_{NH}^{(l,l)} & \text{ if  } (u_i,v_i)-(u_j,v_j)=(-1,0)  \text{ and  } u_i < K_{\NH}  \text{ and  } v_i < K_{\RG},\\
 \lambda_{RG}^{(l,l)} & \text{ if  } (u_i,v_i)-(u_j,v_j)=(0,-1)  \text{ and  } u_i < K_{\NH}  \text{ and  } v_i < K_{\RG},\\
\lambda_{NH}^{(l,h)} & \text{ if  } (u_i,v_i)-(u_j,v_j)=(-1,0) \text{ and  } u_i < K_{\NH}  \text{ and  } v_i \geq K_{\RG},\\
\lambda_{RG}^{(l,h)} & \text{ if  } (u_i,v_i)-(u_j,v_j)=(0,-1) \text{ and  } u_i < K_{\NH}  \text{ and  } v_i \geq K_{\RG},\\
\lambda_{NH}^{(h,l)} & \text{ if  } (u_i,v_i)-(u_j,v_j)=(-1,0) \text{ and  } u_i \geq K_{\NH}  \text{ and  } v_i < K_{\RG},\\
\lambda_{RG}^{(h,l)} & \text{ if  } (u_i,v_i)-(u_j,v_j)=(0,-1) \text{ and  } u_i \geq K_{\NH}  \text{ and  } v_i < K_{\RG},\\
\lambda_{NH}^{(h,h)} & \text{ if  } (u_i,v_i)-(u_j,v_j)=(-1,0) \text{ and  } u_i \geq K_{\NH}  \text{ and  } v_i \geq K_{\RG},\\
\lambda_{RG}^{(h,h)} & \text{ if  } (u_i,v_i)-(u_j,v_j)=(0,-1) \text{ and  } u_i \geq K_{\NH}  \text{ and  } v_i \geq K_{\RG},\\
0 & \text{ otherwise}.
\end{cases}
\end{equation}

@@

In particular it can be seen that a value of $t>0.8$ becomes imperative for high demand.
The lowest value of $t$ for which gives PoA$=1$ for the actual demand levels ($x=0$) is in fact $t=0.72$.
It is also noted that as demand increases the effect of uncoordinated behaviour increases (and the recommended target also increases) as shown in Figure \ref{mintargetvdemand}.

@@

Also, for very low values of demand, cooperation can be obtained with no target.
\begin{itemize}
    \item When the demand is low, there is no scope for uncoordinated behaviour to be damaging.
    \item When the demand is very high, the system is saturated and once again uncoordinated behaviour has no negative effect in comparison to optimal behaviour.
    \item There is however a region of demand for which there is a high PoA.
\end{itemize}

@@

A result is proved that allows for the assertion of existence of a Nash Equilibrium. This result is then applied to two particular models that are influenced by discussions with a local health board:

\begin{itemize}
\item Strict diversion: patients can be lost to the system if both CCUs declare being in diversion.
\item Soft diversion: if both CCUs are in diversion then they cannot divert their own patients.
\end{itemize}

>>>>

The paper is organised as follows: Section \ref{queueingandgamemodels} presents
the general methodology as well as a theoretical existence condition for Nash
Equilibrium. Section \ref{results} presents the findings from two models.
Finally, conclusions and further ideas for progression are given in Section
\ref{conclusions}.

@@

The state space for the Markov chain is given by (\ref{statespace}).

@@

The stochastic transition rate matrix $Q=Q(c_{NH},c_{RG})$ of the continuous-time Markov chain \cite{Stewart2009} has entries $q_{ij}=q_{(u_i,v_i),(u_j,v_j)}$ which is the rate at which a transition from state $i$ to state $j$ occurs. The transition rates are given by (\ref{transitions}) and are illustrated diagrammatically in Figure \ref{mc}.

\begin{equation}
q_{(u_i,v_i),(u_j,v_j)}=\begin{cases} u\mu_{\NH} & \text{ if  } (u_i,v_i)-(u_j,v_j)=(1,0),\\
 v\mu_{\RG} & \text{ if  } (u_i,v_i)-(u_j,v_j)=(0,1),\\
 \lambda_{NH}^{(l,l)} & \text{ if  } (u_i,v_i)-(u_j,v_j)=(-1,0)  \text{ and  } u_i < K_{\NH}  \text{ and  } v_i < K_{\RG},\\
 \lambda_{RG}^{(l,l)} & \text{ if  } (u_i,v_i)-(u_j,v_j)=(0,-1)  \text{ and  } u_i < K_{\NH}  \text{ and  } v_i < K_{\RG},\\
\lambda_{NH}^{(l,h)} & \text{ if  } (u_i,v_i)-(u_j,v_j)=(-1,0) \text{ and  } u_i < K_{\NH}  \text{ and  } v_i \geq K_{\RG},\\
\lambda_{RG}^{(l,h)} & \text{ if  } (u_i,v_i)-(u_j,v_j)=(0,-1) \text{ and  } u_i < K_{\NH}  \text{ and  } v_i \geq K_{\RG},\\
\lambda_{NH}^{(h,l)} & \text{ if  } (u_i,v_i)-(u_j,v_j)=(-1,0) \text{ and  } u_i \geq K_{\NH}  \text{ and  } v_i < K_{\RG},\\
\lambda_{RG}^{(h,l)} & \text{ if  } (u_i,v_i)-(u_j,v_j)=(0,-1) \text{ and  } u_i \geq K_{\NH}  \text{ and  } v_i < K_{\RG},\\
\lambda_{NH}^{(h,h)} & \text{ if  } (u_i,v_i)-(u_j,v_j)=(-1,0) \text{ and  } u_i \geq K_{\NH}  \text{ and  } v_i \geq K_{\RG},\\
\lambda_{RG}^{(h,h)} & \text{ if  } (u_i,v_i)-(u_j,v_j)=(0,-1) \text{ and  } u_i \geq K_{\NH}  \text{ and  } v_i \geq K_{\RG},\\
0 & \text{ otherwise}.
\end{cases}
\label{transitions}
\end{equation}

@@

In particular it can be seen that a value of $t>0.8$ becomes imperative for high demand.
The lowest value of $t$ which gives PoA$=1$ for the actual demand levels ($x=0$) is in fact $t=0.72$.
It is also noted that as demand increases the effect of uncoordinated behaviour increases (and the recommended target also increases) as shown in Figure \ref{mintargetvdemand}. This is potentially due to the fact that as demand increases there is the scope for larger discrepancy between optimal and sub optimal behaviours.

@@

Also, for very low values of demand, cooperation can be obtained with no
target.  When the demand is low, there is no scope for uncoordinated behaviour
to be damaging.  When the demand is very high, the system is saturated and once
again uncoordinated behaviour has no negative effect in comparison to optimal
behaviour.  There is however a region of demand for which there is a high PoA.

@@

A result is proved that allows for the assertion of existence of a Nash
Equilibrium. This result is then applied to two particular models that are
influenced by discussions with a local health board. \textbf{Strict diversion}:
patients can be lost to the system if both CCUs declare being in diversion.
\textbf{Soft diversion}: if both CCUs are in diversion then they cannot divert
their own patients.
